---
title: "Evidence-to-decision tool summary"
date: "`r format(Sys.time(), '%d-%B-%Y')`"
mainfont: Verdana
output:
  pdf_document: default
  word_document:
    reference_docx: "customrep.docx"
---

### Name
`r paste(p(input$reportname))`

### Organisation
`r paste(p(input$reportorgname))`

# 1. Define the Decision Context

### What is the problem?
`r paste(p(input$action01))`

### Location
`r paste(p(input$action02))`

### What is the ultimate goal?
`r paste(p(input$action03))`

### What is the focal target?
`r paste(p(input$action04))`

### What is the relevant ecological, physical, and social context underlying the decision? What constraints are there on your decision-making?
`r paste(p(input$action05))`

\newpage

# 2. Gather Evidence

## Potential actions
`r paste(p(input$action06))`

\newpage

```{r results ="asis", echo=FALSE}
report_text<-textsummary()
for(i in 1:length(report_text)){
  cat(report_text[[i]])
}
```

\newpage

# 3. Make an Evidence-Based Decision
### Summary assessment table for each action 
Table legend: White = Very low certainty or unsure. Pale yellow = Low certainty. Yellow = Moderate certainty. Gold = High certainty.
```{r chunklabel, dev='png', fig.align="left", fig.dim=c(3,0.5),out.width="100%",out.height="100%",dpi=300,echo=FALSE, cache=FALSE, warning = FALSE, message = FALSE, tidy=TRUE} 
library(DT) 
library(webshot) 
if(is.null(webshot:::find_phantom())){webshot::install_phantomjs()} 
idlist <- updateidlist$data
if(length(idlist)>0){
    actnames<-lapply(1:length(idlist),
                       function(i){data.table("Action"=idlist[i],
                                              "Local Effectiveness (scientific literature)"=input[[glue("actioneff",idlist[i])]],
                                              "Local Effectiveness (own data & monitoring)"=input[[glue("actioneffown",idlist[i])]],
                                              "Local Effectiveness (undocumented knowledge)"=input[[glue("actioneffknow",idlist[i])]],
                                              "Cost-effectiveness"=input[[glue("actioncost1",idlist[i])]],
                                              "Wider costs, risks, & benefits"=input[[glue("actioncost2",idlist[i])]],
                                              "Acceptability"=input[[glue("actionacc",idlist[i])]],
                                              "Feasibility"=input[[glue("actionfeas",idlist[i])]],
                                              "Modification potential"=input[[glue("actionmod",idlist[i])]],
                                              "Local Effectiveness Certainty (scientific literature)"=input[[glue("actioneffcert",idlist[i])]],
                                              "Local Effectiveness Certainty (own data & monitoring)"=input[[glue("actioneffcertown",idlist[i])]],
                                              "Local Effectiveness Certainty (undocumented knowledge)"=input[[glue("actioneffcertknow",idlist[i])]],
                                              "Cost-effectiveness Certainty"=input[[glue("actioncost1cert",idlist[i])]],
                                              "Wider costs, risks, & benefits Certainty"=input[[glue("actioncost2cert",idlist[i])]],
                                              "Acceptability Certainty"=input[[glue("actionacccert",idlist[i])]],
                                              "Feasibility Certainty"=input[[glue("actionfeascert",idlist[i])]],
                                              "Modification potential Certainty"=input[[glue("actionmodcert",idlist[i])]]
                                     )})
    table1 <- data.table(do.call(rbind,actnames))
    colvalscert <-  c("#FFFFFF","#FFFFCC","#FFFF80","#FFCC00","#FFFFFF")
    colvalnames <- c("Very low","Low","Moderate","High","Unsure")
    datatable(table1,rownames=FALSE,height="100%",
              extensions=c('ColReorder','Responsive','FixedHeader'),
              options = list(searching=FALSE, paging=FALSE, info=FALSE,
                fixedHeader = TRUE,
                scrolly = TRUE,
                colReorder = TRUE,
                columnDefs = list(list(className = 'dt-center', targets = 0:8),list(visible=FALSE,targets=9:16)) # columns aligment to center, javascript starts at 0 not 1!
              ),
              editable="cell"
    ) %>% formatStyle(columns="Local Effectiveness (scientific literature)", valueColumns="Local Effectiveness Certainty (scientific literature)", backgroundColor = styleEqual(colvalnames,colvalscert))%>%
      formatStyle(columns="Local Effectiveness (own data & monitoring)", valueColumns="Local Effectiveness Certainty (own data & monitoring)", backgroundColor = styleEqual(colvalnames,colvalscert))%>%
      formatStyle(columns="Local Effectiveness (undocumented knowledge)", valueColumns="Local Effectiveness Certainty (undocumented knowledge)", backgroundColor = styleEqual(colvalnames,colvalscert))%>%
     formatStyle(columns="Cost-effectiveness", valueColumns="Cost-effectiveness Certainty", backgroundColor = styleEqual(colvalnames,colvalscert))%>%
      formatStyle(columns="Wider costs, risks, & benefits", valueColumns="Wider costs, risks, & benefits Certainty", backgroundColor = styleEqual(colvalnames,colvalscert))%>%
        formatStyle(columns="Acceptability", valueColumns="Acceptability Certainty", backgroundColor = styleEqual(colvalnames,colvalscert))%>%
          formatStyle(columns="Feasibility", valueColumns="Feasibility Certainty", backgroundColor = styleEqual(colvalnames,colvalscert))%>%
            formatStyle(columns="Modification potential", valueColumns="Modification potential Certainty", backgroundColor = styleEqual(colvalnames,colvalscert))
    }
if(length(idlist)==0){
    table1 <- data.frame(cbind(rep("Start assessing actions in the tool to display a summary output here."),"","","","","","","",""))
    colnames(table1)<- c("Action","Local Effectiveness (scientific literature)","Local Effectiveness (own data & monitoring)","Local Effectiveness (undocumented knowledge)", "Cost-effectiveness", "Wider costs, risks, & benefits", "Acceptability","Feasibility","Modification potential")
    datatable(table1,rownames=FALSE,height="100%",
              extensions=c('ColReorder','Responsive','FixedHeader'),
              options = list(searching=FALSE, paging=FALSE, info=FALSE,
                fixedHeader = TRUE,
                scrolly = TRUE,
                colReorder = TRUE)
              
    )
  }
```

### Which action(s), if any, are the best ones to implement to achieve the ultimate goal(s) you defined at the beginning? Name and justify your choices.
`r paste(p(input$action20))`

### Which action(s) should not be implemented? Name and justify your choices.
`r paste(p(input$action21))`

### What is your overall decision, what are the next steps, and why?
`r paste(p(input$action22))`


